Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
Use \linewidth over 0.5\textwidth.

\title{{\color {red}better title eventually}}
\author{Linda N. Lee, David Fifield\\
University of California, Berkeley, \{lnl, fifield\}@cs.berkeley.edu
}
\maketitle

@@

While our pilot was insightful, the experiment itself is not very reproducible, as it requires
a specific target audience (journalists who have recently reported in other countries) along 
with specific guidance and feedback on how to perform a cognitive walkthrough. This makes it hard
for the research community to prove or build on any findings. Therefore, we take precautions
to ensure that our full-scale study will be reproducible.

@@

@@

\begin{figure}[t]
\includegraphics[width=0.5\textwidth]{configuration-dialog.png}
\caption{The fourth and final window of the Tor configuration dialog is what users will use to 
configure their network settings to circumvent censorship. The instructions asks users to 
choose a pluggable transport or enter custom bridges.}
\label{dialog}
\end{figure}

@@

\subsection{Usability work on Tor}
\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
has led to great usability improvements ~\cite{clark2007usability}.  Clark analyzed the challenges 
of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
none are fully satisfactory from a usability perspective. Researchers provide guidelines on 
how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
usable security and computer human interaction. Key takeaways from this work includes 
finding out that exposure to how Tor works may be difficult for users to understand, and that 
familiar, non-technical language is critical for communication. We plan to draw from Clark's
guidelines as well as other works in usable security and computer human interaction to suggest
any improvements to the Tor Browser.

@@

\subsection{Usable Security and User Behavior} %%%%%%
\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.}

{\color {red}  I guess that other literature on general usability applies here too.
Especially look into browser configuration work. }

@@

\section{UX sprint} %%%%%%
\label{sec:pilot}
 {\color {red}  Talk about why we did what we did, and what the end goal 
of the experiment was. Also talk about how we expected users
to be much better at installing and downloading than they were. }

@@

\subsection{Methodology} %%%%%%%%%
We 
{\color {red} How we recruited, what the setup was like, how we got the tasks, details of 
how the experiment was run, and things like that.}

\subsection{Results}
\indent \indent Because of the limited size of the study, it's not possible to state with confidence what 
fraction of users will encounter major usability obstacles. However, it was effective at discovering 
and demonstrating issues that are likely to cause problems for many users. For specific problems 
encountered by an individual user, we refer you to our resources below.

>>>>

\title{Assessing Tor's Usability as a Censorship Circumvention Tool}
\author{Linda N. Lee, David Fifield\\
University of California, Berkeley, \{lnl, fifield\}@cs.berkeley.edu
}
\maketitle

@@

@@

\subsection{Assumptions} 
{\color{red} do I need this here?}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{configuration-dialog.png}
\caption{The fourth and final window of the Tor configuration dialog is what users will use to 
configure their network settings to circumvent censorship. The instructions asks users to 
choose a pluggable transport or enter custom bridges.}
\label{dialog}
\end{figure}

@@

\subsection{Usability Work on Tor}
\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
has led to great usability improvements ~\cite{clark2007usability}.  Clark analyzed the challenges 
of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
none are fully satisfactory from a usability perspective. Researchers provide guidelines on 
how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
usable security and computer human interaction. Key takeaways from this work includes 
finding out that exposure to how Tor works may be difficult for users to understand, and that 
familiar, non-technical language is critical for communication. We plan to draw from Clark's
guidelines as well as other works in usable security and computer human interaction to suggest
any improvements to the Tor Browser.

@@

\subsection{Usable Security and User Behavior} %%%%%%
% Okay, this is a mess. Last brain dump before sleep. 
\indent \indent {\color {red} 
The work that started usable security, using a cognitive walkthough to expose usability issues
in PGP ~\cite{whitten1999johnny}. The authors give suggestions for better usability, such as 
aligning words to pictures, etc.

 Work which shows that people are willing to give up privacy for instant gratification with respect to 
 e-commerce, showing that participants' motivations are not aligned for preserving privacy, but to 
 complete the task at hand. ~\cite{acquisti2004privacy}. Talk about how censorship might be different
 because people need to actually configure to succeed.

 People care about how easy something is to use when picking software ~\cite{}.

 infrastructure is highly distributed, with the bundle of
tools in one single installer (below is the screenshot of
the Vidalia control panel, which runs on many different
platforms), making the technology accessible to average
users BUt people don't care.

 users should not only look at the technical angle of their
approach, but should also be aware of frequent attempts
to infiltrate or otherwise identify social networks of
people with dissenting opinions, even when they are
only partially operating online.

you might want to choose a system based on the usability of others 
~\cite{dingledine2006anonymity}.

  }

@@

\section{UX sprint} %%%%%%
\label{sec:pilot}
\indent \indent This pilot was to test-drive an experiment which examines the usability of Tor as an anonymity tool
with respect to a target demographic of users known to use Tor (journalists who have reported in other
countries). We emphasized the targeting of a high-risk user group of Tor and to 
target usability changes aimed at helping those who could not afford to make mistakes. To see 
if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
we created tasks to licit Tor's non-typical behaviors and ask our participants to
navigate through more advanced settings.

@@

\subsection{Methodology} 
\indent \indent We recruited five journalists from Berkeley by reaching out to journalist contacts.
 We recruited five users with an average age of 28 ($\sigma = 13 $~years). Out of 
our five participants, 3 were female.

We conducted the experiment on January 30-31st in Soda 
Hall at the University of Berkeley, California. We used a 2013 Macbook Air and a 
2012 Acer Aspire AS5750Z-4835 Windows laptop to give users a choice in using whatever they were comfortable with. 
All of our participants were Mac users. During the experiment, 
we recorded video data of their computer screen and audio data to capture their cognitive walkthrough. 
The average time to complete the given tasks, not including the cognitive
walkthrough nor the exit survey, was 26 minutes ($\sigma = 7$~min).

This pilot was held in conjunction with the first Tor UX sprint. With IRB approval, Tor developers
observed the screens of our participants, which was set to broadcast to a separate  
room during the experiment. Audio of the cognitive walkthrough was not broadcast for privacy
considerations as voice is considered an identifying characteristic.

\subsection{Results}
\indent \indent Because of the limited size of the study, it's not possible to state with confidence what 
fraction of users will encounter major usability obstacles. However, it was effective at discovering 
and demonstrating issues that are likely to cause problems for many users. 
People did have difficulty with installing Tor Browser (principally because of the Gatekeeper 
code-signing feature on OS X), did not understand what many of the toolbar options meant, 
and were confused by most Tor-specific behaviors. For specific problems 
encountered by an individual user, we refer you to our resources below.
